Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-09 main.tex
Added Deanna and Aude as co-authors

\author{S\'everin Lemaignan, Alexis Jacq, Fernando Garcia, Ana Paiva, Pierre
Dillenbourg \\ CHILI Lab, \'Ecole Polytechnique F\'ed\'erale de Lausanne}

@@

We would like to thank Deanna Hood for her key contribution to the project.
This research was partially supported by the Funda\c{c}\~{a}o para a Ci\^{e}ncia
e a Tecnologia (FCT) with reference UID/CEC/50021/2013, and by the Swiss
National Science Foundation through the National Centre of Competence in
Research Robotics.

>>>>

\author{S\'everin Lemaignan$^1$, Alexis Jacq$^{1,2}$, Fernando Garcia$^1$,
    Deanna Hood$^1$, \\Aude
    Billard$^1$, Ana Paiva$^2$, Pierre Dillenbourg$^1$ \\
$^1$CHILI Lab, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Suisse,\\
$^2$Instituto Superior T\'{e}cnico, University of Lisbon, Portugal}

@@

This research was partially supported by the Funda\c{c}\~{a}o para a Ci\^{e}ncia
e a Tecnologia (FCT) with reference UID/CEC/50021/2013, and by the Swiss
National Science Foundation through the National Centre of Competence in
Research Robotics.
